Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-25 WSSSPE1_report/WSSSPE1_summary_report.tex
fix a typo, add some non-linebreaking spaces

\subsubsection{Licensing and Software Patents}
Software is no longer either open or closed (only binaries available),
but also licensed and patented, which clearly also impact 
software sustainability.
While many papers briefly discussed licensing issues,
Elster~\cite{Elster_WSSSPE} directly discussed the impact of software licenses 
on obtaining industrial funding for scientific software
projects.  In particular, she describes her experiences with researchers
unwilling to utilize GPL (copyleft) code, as it adds restrictions to
reuse that they themselve as we well as some industries find unacceptable for future
commercialization.  (This was discussed by Hanwell et
al.~\cite{Hanwell_WSSSPE} as well.)  US ICT companies funding 
academics will thus often insist on BSD licensing on software 
since they then can legally include the code into their commercial
codes.

On the other hand, there are companies
that fund larger GPL-licensed software projects \cite{Blatt_WSSSPE}
that insists that the university projects they fund 
also produce code with GPL licensing.
They do not accept BSD-like licenses since they argue that
other companies then may choose to build closed commercial
codes on they software they funded, rather than encouraging 
the community to contribute freely and thus ensuring software 
sustainability for the community.

@@

Elster \cite{Elster_WSSSPE} also points out how the 
prevalence and rapid growth of multi and many-core systems forces 
awareness of data locality and synchronization issues
if one want to teach people how to develop high-performing scientific codes.

>>>>

\subsubsection{Licensing and Software Patents}
Software is no longer either open or closed (only binaries available),
but also licensed and patented, which clearly also impact 
software sustainability.
While many papers briefly discussed licensing issues,
Elster~\cite{Elster_WSSSPE} directly discussed the impact of software licenses 
on obtaining industrial funding for scientific software
projects.  In particular, she describes her experiences with researchers
unwilling to utilize GPL (copyleft) code, as it adds restrictions to
reuse that they themselve as well as some industries find unacceptable for future
commercialization.  (This was discussed by Hanwell et
al.~\cite{Hanwell_WSSSPE} as well.)  US ICT companies funding 
academics will thus often insist on BSD licensing on software 
since they then can legally include the code into their commercial
codes.

On the other hand, there are companies
that fund larger GPL-licensed software projects~\cite{Blatt_WSSSPE}
that insists that the university projects they fund 
also produce code with GPL licensing.
They do not accept BSD-like licenses since they argue that
other companies then may choose to build closed commercial
codes on they software they funded, rather than encouraging 
the community to contribute freely and thus ensuring software 
sustainability for the community.

@@

Elster~\cite{Elster_WSSSPE} also points out how the 
prevalence and rapid growth of multi and many-core systems forces 
awareness of data locality and synchronization issues
if one want to teach people how to develop high-performing scientific codes.
